``FISTA'' in Banach spaces with adaptive discretisations

### 2021-08-05 response.tex

We would like to thank both the reviewers for their time and feedback. All changes are marked in the supplementary pdf and a detailed response to each reviewer is given below.

\section{Detailed response to first reviewer}

\begin{enumerate}
	\item \review{The authors base much of the analysis on the objective function and its convergence properties \ldots it would be interesting to know how the solutions $w_n$ converge for the various versions of FISTA.}

	We thank the reviewer for their suggestion but it seems quite challenging to make a general statement. As in your comment, if one has coercivity then the convergence is clear. More generally, FISTA is known to converge weakly in the Hilbert-space setting. This is also likely to hold with our algorithm when the minimiser is in $\F H$ but we have not performed the analysis as it is still a relatively special case. A key component of the proof is the bound $\lVert u_n-u_{n-1}\rVert = o(n^{-1})$, in general we do not even expect this quantity to be bounded. It's not clear whether we can leverage the Hilbert-norm structures of FISTA to gain any convergence in the Banach space.

	\todo{Not sure if this is the right level of detail.}

@@

	\item \review{On page 18, the authors state: Suppose that the numerical aim is to find a function $u_n$ with $E_0(u_n)\leq 0.1$, all methods would converge after $O(10^3)$ iterations, demonstrating some equivalence between the two FISTA algorithms}

	\review{This is used to argue that the adaptive schemes are better as they require smaller problems, less memory and less time to get to this point. However, it would appear that Figure 2 indicates that if a sufficiently accurate solution were desired, instead of a point with $E_0(u_n)\leq 0.1$, then we would still need orders of magnitude of 10 more iterations to get to the same accuracy as the nonadaptive schemes.}

	The convergence displayed in Figure 2 is relative to the discretised problem, rather than the continuous one. The behaviour for the continuous gap is shown in Figure 3 (for two of the algorithms from Figure 2). Figure 2 shows that the nonadaptive schemes reach high precision very quickly, but Figure 3 indicates that this does not correlate with accuracy.

	\todo{I could include extra continuous gap (like Figure 1) panels? Or just show continuous gap? At the moment it's perhaps a bit confusing, figures (1,2,3,4,7,9) show (both, discrete, continuous, continuous, discrete, continuous) respectively. It might be simpler to show only the continuous gap except in Figure 1 (which compares both).}
\end{enumerate}

### 2021-08-05 paper.tex
minor update

	In higher dimensions, the only two things which change are the number of children ($2^d$ for non-leaves) and at each node you store the coefficients of $2^d-1$ wavelets. The support on each node is still a disjoint partition of unity consisting of regular cubes of side length $2^{-k}$ at level $k$. The only change in our own implementation is to translate the support to $[-\tfrac12,\tfrac12]^2$. We briefly remark that the tree structuring of wavelets is not novel and appears more frequently in the Bayesian inverse problems literature \cite{Castillo2019}.

>>>>

	In higher dimensions, the only two things which change are the number of children ($2^d$ for non-leaves) and at each node you store the coefficients of $2^d-1$ wavelets. The support on each node is still a disjoint partition of unity consisting of regular cubes of side length $2^{-k}$ at level $k$. The only change in our own implementation is to translate the support to $[-\tfrac12,\tfrac12]^2$. We briefly remark that the tree structuring of wavelets is not novel and appears more frequently in the Bayesian inverse problems literature \cite{Castillo2019,Kekkonen2021}.
